Evaluation of Cache-Oblivious Data Structures

### 2008-05-25 paper/paper.tex
Added abstract and keywords to paper.

\begin{abstract}
% TODO: rewrite (NB: max. 10 lines)
%In modern computer hardware architecture, memory is organized in a hierarchy
%consisting of several types of memory with different memory sizes, block
%transfer sizes and access times. The cache-oblivious model has been proposed
%to reflect this reality more accurately than traditional models. A number of
%algorithms and data structures have been proposed that perform optimally in
%this model. The goal of the proposed research project is to implement a
%selection of cache-oblivious set-like data structures, evaluate their
%performance (in terms of execution time and memory use) in a realistic
%environment, and compare their performance to traditional data structures.
\end{abstract}

>>>>

\begin{abstract}
In modern computer hardware architecture, memory is organized in a hierarchy
consisting of several types of memory with different memory sizes, block
transfer sizes and access times. To reflect this situation more accurately
than tradition models, the cache-oblivious model has been proposed, and several
algorithms and data structures have been proposed that perform optimally in
this model.
This paper presents the results of an emperical evaluation of various data
structures in a realistic scenario, and gives insight into the applicability
of cache-oblivious data structure in practice.
\end{abstract}
